\documentclass[10pt,-letter paper]{article}
\usepackage[left=1in, right=0.75in, top=1in, bottom=0.75in]{geometry}
\usepackage{graphicx} % Required for inserting images
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
\doublespacing
\singlespacing
\usepackage[none]{hyphenat}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{amsthm}
\interdisplaylinepenalty=2500
%\savesymbol{iint}
\usepackage{txfonts}
%\restoresymbol{TXF}{iint}
\usepackage{wasysym}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{txfonts}
\let\vec\mathbf{}
\usepackage{stfloats}
\usepackage{float}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
\usepackage{amssymb}
%\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{eenrc}
%\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
%\usepackage{listings}
\usepackage[latin1]{inputenc}
%%\usepackage{color}{   
%%\usepackage{lscape}
\usepackage{textcomp}
\usepackage{titling}
\usepackage{hyperref}
%\usepackage{fulbigskip}   
\usepackage{tikz}
\usepackage{graphicx}
\lstset{
  frame=single,
  breaklines=true
}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{siunitx}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tfrupee}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mwe} % for blindtext and example-image-a in example
\usepackage{wrapfig}
\graphicspath{{figs/}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\newcommand{\sgn}{\mathop{\mathrm{sgn}}}
\providecommand{\abs}[1]{\left\vert#1\right\vert}
\providecommand{\res}[1]{\Res\displaylimits_{#1}} 
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
%\providecommand{\norm}[1]{\lVert#1\rVert}
\providecommand{\mtx}[1]{\mathbf{#1}}
\providecommand{\mean}[1]{E\left[ #1 \right]}
\providecommand{\fourier}{\overset{\mathcal{F}}{ \rightleftharpoons}}
%\providecommand{\hilbert}{\overset{\mathcal{H}}{ \rightleftharpoons}}
\providecommand{\system}{\overset{\mathcal{H}}{ \longleftrightarrow}}
 %\newcommand{\solution}[2]{\textbf{Solution:}{#1}}
%\newcommand{\solution}{\noindent \textbf{Solution: }}
\newcommand{\cosec}{\,\text{cosec}\,}
\providecommand{\dec}[2]{\ensuremath{\overset{#1}{\underset{#2}{\gtrless}}}}
\newcommand{\myvec}[1]{\ensuremath{\begin{pmatrix}#1\end{pmatrix}}}
\newcommand{\myaugvec}[2]{\ensuremath{\begin{amatrix}{#1}#2\end{amatrix}}}
\newcommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\begin{document}
\title{assignment}
\date{\today}
\maketitle
\section*{CBSE 2018 Mathematics Questions: 65.4.2}
\subsection*{Matrices}
\begin{enumerate}
\item If A is a square matrix of order $3$, $|A|=9$,then write the value of $|2.\text{adj} A|$.
\item If $A$ and $B$ are symmetric matrices, such that $AB$ and $BA$ are both defiend, then prove that $AB-BA$ is a skew symmetric matricx.
\subsection*{Vectors}
\item Find the acute angle between the planes $\overrightarrow{r}.(\hat{i}-2\hat{j}-2\hat{k})=1$ and $\overrightarrow{r}.(3\hat{i}-6\hat{j}+2\hat{k})=0$.
\item $\vec{X}$ and $\vec{Y}$ are two points with position vectors $3 \overrightarrow{a} + \overrightarrow{b}$ and $\overrightarrow{a} - 3 \overrightarrow{b}$ respectively. Write the position vector of a point $\vec{Z}$ which divides the line segment $XY$ in the ratio $2$:$1$ externally.
\item Let $\overrightarrow{a}=\hat{i}+2\hat{j}-3\hat{k}$ and $\overrightarrow{b}=3\hat{i}-\hat{j}+2\hat{k}$be two vectors.Show that the vectors $(\overrightarrow{a} + \overrightarrow{b}$ and $(\overrightarrow{a} - \overrightarrow{b})$ are perpendicular to each other.
\item Find the value of $x$, for which the four points $A\brak{x,-1,-1}$, $B\brak{4,5,1}$,$C\brak{3,9,4}$ and $D\brak{-4,4,4}$ are co-planar.
\subsection*{Linear Forms}
\item Find the length of the intercept, cut off by the plane on the x-axis.                                                                             \begin{align*}                                                                2x+y-z=5                                                          \end{align*}                                            
\subsection*{Differentiation}
\item If $y=cosec\hspace{3pt}(\cot\sqrt{x})$, then find $\dfrac{dy}{dx}$.
\item Write the integrating factor of the differential equation $(tan^{-1} y-x) \,dy=(1+y^{2}) \,dx$.
\item Solve the following differential equation: $\dfrac {dx}{dy}+x=(tan y + sec^{2} y).$
\item If $y=(x)^{\cos{x}}+{(\cos{x})}^{\sin{x}},$ find $\dfrac{dy}{dx}.$
\item A ladder $13$ m long is leaning against a vertical wall.The bottom of the ladder is dragged away from the wall along the ground at the rate of $2$ cm/sec. How fast is the height on the wall decreasing when the foot of the ladder is $5$ m away from the wall ?
\subsection*{Probability}
\item $12$ cards numbered $1$ to $12$ (one number on one card), are placed in a box and mixed up thoroughly. Then a card is drawn at random from the box. If it is known that number on the drawn card is greater than $5$, find the probability that the card bears an odd number.
\item Out of $8$ outstanding students of a school, in which there are $3$ boys and $5$ girls, a team of $4$ students is to be selected for a quiz competition. Find the probability that $2$ boys and $2$ girls are selected.
\item In a multiple choice examination with three possible answers for each of the five questions, what is the probability that a candidate would get four or more correct answerrs just by guessing ?
\subsection*{Integration}
\item Find: $\displaystyle \int x.tan^{-1} x \,dx$
\item Find: $\displaystyle \int \dfrac{dx}{\sqrt{5-4x-2x^{2}}}.$
\item Find: $\displaystyle \int_{\frac{-\pi}{4}}^{0}$ $\dfrac{1+tanx}{1-tanx} \,dx.$
\item Prove that $\int_{0}^{a}f(x) \,dx=\int_{0}^{a}f(a-x) \,dx$, and hence evaluate $\int_{0}^{1}x^{2}(1-x)^{n} \,dx.$
\subsection*{Functions}
\item Let $\ast : N \times N \rightarrow N$ be an operation defined as $a \ast b= a+ ab,\forall a,b \in N$. Check if $\ast$ is binary operation. If yes, find if it is associative too.
\end{enumerate}
\end{document}
